Ring of Fire Camera Detections Report

### 2023-02-23 analysis/paper/paper.qmd
update

- Add explanation about image bursts and upload of bursts including empties

>>>>

Finally, it is important to note that not only pictures with detections were uploaded to the platform. Because camera traps produce images in bursts, we included all the pictures from a given bursts if any of the images in the bursts include a detection with certainty above the threshold.
